Minimizing post-shock forecasting error through aggregation of outside information

### 2020-08-29 Submission/manuscript.tex
addition of codes and mentions in manuscript

Supplementary material includes the results of  likelihood ratio test for  independence among nested shock effects in Section \ref{forecasting}, the algorithmic formulation of $\mc{B}_u$ and $\mc{B}_f$, simulation results for $\mc{M}_1$, and simulation results for an example of the boundary case $p < n$.

>>>>

Supplementary material includes the results of  likelihood ratio test for  independence among nested shock effects in Section \ref{forecasting}, the algorithmic formulation of $\mc{B}_u$ and $\mc{B}_f$, simulation results for $\mc{M}_1$, simulation results for an example of the boundary case $p < n$, and R codes for corresponding simulations and data analysis.
